The Local Group in the Cosmic Web

### 2014-10-09 paper/main.tex
updated caption in figure 3 and 4
updated captions

\begin{figure*}
\begin{center}
  \includegraphics[width=0.32\textwidth]{fig3a.pdf}
  \includegraphics[width=0.32\textwidth]{fig3b.pdf}
  \includegraphics[width=0.32\textwidth]{fig3c.pdf}
\end{center}
\caption{Cumulative distributions for the alignment between the normal
  vector to the pair orbital plane, $\hat{n}$, and the three eigenvectors in
  the Tweb.
    \label{fig:alignment_n}}  
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.32\textwidth]{fig4a.pdf}
  \includegraphics[width=0.32\textwidth]{fig4b.pdf}
  \includegraphics[width=0.32\textwidth]{fig4c.pdf}
\end{center}
\caption{Cumulative distributions for the alignment between the vector
  linking the two halos in the pair, $\hat{r}$, and the three
  eigenvectors in the Tweb.
    \label{fig:alignment_r}}  
\end{figure*}

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{fig5.pdf}
\caption{Mass dependency of the median value for the dot product
  between the normal vector $\hat{n}$ and each one of the
  eigenvectors.  The lines show the trends for the general sample.
The error bars in the 2$\sigma$ and 3$\sigma$ points
  correspond to jackknife estimates. 
\label{fig:median_alignment_n}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{fig6.pdf}
\end{center}
\caption{Alignment between the two angular momentum vectors of the two
  halos in the pair.
    \label{fig:jj_alignment}}  
\end{figure}

>>>>

\begin{figure*}
\begin{center}
  \includegraphics[width=0.32\textwidth]{fig3a.pdf}
  \includegraphics[width=0.32\textwidth]{fig3b.pdf}
  \includegraphics[width=0.32\textwidth]{fig3c.pdf}
\end{center}
\caption{Cumulative distributions for the alignment between the normal
  vector to the pair orbital plane, $\hat{n}$, and the three eigenvectors in
  the Tweb. 
The shaded region shows the expectation for a random
  distribution without any preferential alignment, it encloses the $5\%$ and $95\%$ percentiles of 5000
  flat distributions for $\mu$ generated with the  same number of
  points as the $2\sigma$ sample.  
    \label{fig:alignment_n}}  
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.32\textwidth]{fig4a.pdf}
  \includegraphics[width=0.32\textwidth]{fig4b.pdf}
  \includegraphics[width=0.32\textwidth]{fig4c.pdf}
\end{center}
\caption{Cumulative distributions for the alignment between the vector
  linking the two halos in the pair, $\hat{r}$, and the three
  eigenvectors in the Tweb. The shaded region is the same as in
  Figure \ref{fig:alignment_n}.
    \label{fig:alignment_r}}  
\end{figure*}

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{fig5.pdf}
\caption{Mass dependency of the median value for the dot product
  between the normal vector $\hat{n}$ and each one of the
  eigenvectors.  The lines show the trends for the general sample.
The error bars in the 2$\sigma$ and 3$\sigma$ points
  correspond to jackknife estimates. 
 The shaded region shows the expectation for a random distribution
 without any preferential alignment, it encloses the $5\%$ and $95\%$
 percentiles of 5000  flat distributions for $\mu$ generated with the
 same number of points as the $2\sigma$ sample.   
\label{fig:median_alignment_n}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{fig6.pdf}
\end{center}
\caption{Alignment between the two angular momentum vectors of the two
  halos in the pair.
  The shaded region shows the expectation for a random
  distribution without a preferential alignment as it is described in
  Figure \ref{fig:median_alignment_n}.
    \label{fig:jj_alignment}}  
\end{figure}
